\documentclass [a4paper, 11pt]{article}
\usepackage{comfortaa}
%\renewcommand*\familydefault{\sfdefault} 
%\renewcommand*\rmdefault{ppl}
\renewcommand*\rmdefault{iwona}
\usepackage[T1]{fontenc}
\usepackage[none]{hyphenat}
\usepackage{color}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{sectsty}
\usepackage[a4paper, margin=2cm]{geometry}

\linespread{0.9}

\newcommand{\linedparagraph}[1]{\paragraph{#1}\mbox{}\\}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\renewcommand{\arraystretch}{1.2}

\setlength{\tabcolsep}{.5cm}

\pagenumbering{gobble}

%Ejemplos de macros
% para definir macros inteligentes que anden bien, o sea que terminen con \xspace
\newcommand{\MACRO}[2]{\newcommand{#1}{#2\xspace}}
\newcommand{\MACROP}[3]{\newcommand{#1}[#2]{#3\xspace}}

\newcommand{\tabu}{\hspace*{0.7cm}}
\newcommand{\ctabu}{\hspace*{0.8cm}}
\newcommand{\htabu}{\hspace*{0.35cm}}

\begin{document}

\noindent \begin{tabularx}{\textwidth}{X r}
  \hspace{-15pt}\parbox[t]{15cm}{
  \hspace{-2pt}\textbf{\huge{Melanie Sclar}} \\
  Computer Scientist, University of Buenos Aires \\
  \emph{ \textcolor{gray}{melaniesclar@gmail.com} }
  } &

\parbox[t]{3.8cm}{ \emph{\textcolor{gray}{
  (+54)-911-6527-6507 \\
  (+54)-11-4581-2987 }}
  
}
\end{tabularx}

\sectionfont{\sectionrule{0pt}{0pt}{-.2cm}{1pt}}
\section* {Summary}
Computer Scientist, Latin American champion in the 39th ACM-ICPC World Finals, Mathematics olympiad champion and former Facebook intern. Experienced in problem solving and complex algorithms and looking forward to expanding my knowledge and improving my skills in the field.

\section* {Work Experience}

\begin{description}
  \item[Software Engineer Intern at Facebook Inc.] {\hfill January - April 2016\\
  Worked in the Video Encoding Team, on video stabilization algorithms. Researched various methods to understand when stabilization is necessary or not and saving computing time when it is not needed. %This unnecessary processing can be very prejudicial since they can deform the video and lower its quality.

Uniformed the formats of all videos on the site, which varied along the company's development. This heterogeneity of formats used to have various unwanted consequences on the system, which I fixed during the internship.
}

  \item[Software Engineer Intern at Facebook Inc.] {\hfill January - April 2015\\
Worked in the Public Content Ranking Team, developing algorithms to improve the quality of recommendations on videos and articles shown in newsfeed. These algorithms were based on sentiment analysis and trending topic detection. %These recommendations are other videos related to the original one and are shown to the user when he or she starts watching a video.
}

  \item[Teacher Assistant at University of Buenos Aires] {\hfill March 2014 - July 2017\\
  Responsible for assisting students with their inquiries (involving class projects and 
  exercises) and grading exams and projects. Taught mainly in Algorithms 
  and Data Structures III.
}

\item[Coach for Mathematics Olympiads] {\hfill March 2012 - October 2016 \\ 
\textbf{\small Argentine Model School (2013-2016), Martin Buber School (2013), Carlos Pellegrini School (2012)} \\
%\item[Coach for Mathematics Olympiads in:]
%\item[\tabu Argentine Model School (EAM)] {\hfill March 2013 - October 2016}
%\item[\tabu Martin Buber School] {\hfill March - December 2013}
%\item[\tabu Superior School in Commerce ``Carlos Pellegrini'' (ESCCP)] { \hfill March - December 2012 \\
Helped students acquire problem solving techniques and mathematical concepts necessary in Mathematics Olympiads, and stimulated them to continue researching and solving problems on their own.
	}

\end{description}

\section* {Honors and Awards}

\subsection* {International Awards}

\begin{itemize} \itemsep.05cm
	\item[] Latin American Champion and First to Solve Problem F award in the 39th Annual World Finals of the ACM International Collegiate Programming Contest (ACM-ICPC) in Marrakech, Morocco (2015).
%	\item[] Contestant in the 38th Annual World Finals of the ACM International Collegiate Programming Contest (ACM-ICPC) in Ekaterinburg, Russia (2014).
	\item[] Champion in the South America/South Regional Contest of the ACM-ICPC (2013 and 2014).
	\item[] Third place in the South America/South Regional Contest for the ACM-ICPC (2012).
	\item[] Bronze Medal in the 26th Iberoamerican Mathematical Olympiad (2011) in San Jose, Costa Rica.
	\item[] Silver Medal in the 21st Southamerican Mathematical Olympiad (2010) in S\~ao Paulo, Brazil. 
\end{itemize}

\subsection* {National Awards in Argentina}

\begin{itemize} \itemsep.05cm
    \item[] First, third and second place in Argentine Programming Tournament (TAP) (2014, 2013 and 2012 respectively).
    \item[] Second place in the Interuniversity Argentine Mathematics Competition (CIMA) (2016).
	\item[] National Champion in Argentine Olympiad in Mathematics (OMA) (2011).
	\item[] National Subchampion in Argentine Olympiad in Mathematics (OMA) (2008).
	
\end{itemize}

\newpage
\section* {Patents}
Sclar M, Puntambekar A, Coward MH, Parsons-Keir, WD, inventors; Facebook Inc,
assignee. $(1)$ Foreground detection for video stabilization and $(2)$ A neural network to optimize video stabilization parameters. Attorney Docket Numbers 060406-8393.US00 and 060406-8394.US01, filed on June 30, 2016. Patent pending.
%(1) FOREGROUND DETECTION FOR VIDEO STABILIZATION (2) A NEURAL NETWORK TO OPTIMIZE VIDEO STABILIZATION PARAMETERS
% 060406.8393-8394.US01
% 060406-8393.US00

\section* {Volunteer experience}
\begin{description}
\item[Organizer and teacher of programming competitions' training events] {\hfill July 2014 - ongoing \\
  Taught in four two-week long events aimed at university students that 
  want to improve their skills in competitive programming, as well as 
  several events aimed at high school students. 
}
\item[Organizer of programming and mathematical competitions] { \hfill July 2012 - ongoing \\
}
\end{description}

\section* {Education}
\begin{description}
  \item[University of Buenos Aires]{\hfill 2012-2017 \\
	Licenciada en Ciencias de la Computaci\'on, \\
	equivalent to Bachelor of Computer Science +MSc. G.P.A. 9.65/10 \\
    
    \textbf{Dissertation:} "Analysis and Prediction of Human Visual Search". This project consisted of creating an algorithm involving machine learning and bayesian modelling to predict the most likely paths that human gaze will make when searching for an object in an image.}
% \footnote{Expected graduation date.
  \item[University of Buenos Aires]{\hfill 2012-ongoing \\ 
	Currently pursuing Licenciatura en Ciencias Matem\'aticas, \\
	equivalent to Bachelor of Mathematics +MSc. G.P.A. 9.00/10}
	
  \item[Superior School in Commerce ``Carlos Pellegrini'' - University of Buenos Aires] {\hfill 2007-2011 \\
	High School Degree with Accounting Specialization. G.P.A. 9.02/10}
\end{description}

\section* {Skills}

\begin {tabularx}{\textwidth}{>{\raggedright}>{\bfseries}X p{11.9cm}}
  Algorithms & Experienced due to my participation in informatics olympiads. \\
  Problem Solving & Passionate and highly experienced due to my participation in mathematical and computing olympiads. \\
  Machine Learning & Solid knowledge of the classic supervised and unsupervised models and with experience applying supervised models in structured data and images.
\end {tabularx}

\subsection* {Programming Languages}

\begin {tabularx}{\textwidth}{>{\raggedright}>{\bfseries}X p{11.9cm}}
  C / C++ & Advanced knowledge, 7 years experience \\
  PHP / Hack & Intermediate knowledge, 2 years experience \\
%  Java & Basic knowledge, 2 years experience \\
  Python & Intermediate knowledge, 2 years experience \\
  Haskell & Basic knowledge, 2 years experience \\
%  \\
%  \LaTeX & Intermediate knowledge, 4 years experience
\end {tabularx}

\subsection* {Spoken Languages}

\begin {tabularx}{\textwidth}{>{\raggedright}>{\bfseries}X p{12cm}}
  Spanish & Native Proficiency. \\
  English & Fluent Proficiency, able to use it professionally. \\
  Portuguese & Fluent Proficiency, able to use it professionally. \\
  French & Intermediate Proficiency, able to hold an informal conversation.
\end {tabularx}

\end {document}
